SIMD\slash SIMT-vectorized Sparse Chemical Kinetic Jacobian\slash Thermo-chemical Source-Term Evaluation

### 2018-06-01 paper.tex
tweak wording

In contrast,~\cref{F:pocl_source} shows the mean run time per condition of deep, shallow and unvectorized OpenCL codes on the POCL runtime, as compared to OpenMP parallelization.
No speedup is achieved for either vectorization type on either CPU---\add{though we stress that Intel OpenCL runtime achieved vectorization using the exact same code and hardware}---indeed, the OpenMP case is faster on both CPUs.
The reasons for this lack of vectorization are quite technical,~\delete{and somewhat outside the scope of this work}however \add{personal communications~\cite{pocl_communication} with the developers of POCL revealed that, briefly speaking, substantial changes are required to the way POCL prepares LLVM intermediate-representation code (specifically, to ensure LLVM properly recognizes uniform vectorization loop-bounds), LLVM's handling of branches (potentially within POCL instructions themselves) and memory access patterns and potentially use of relaxed math (i.e., ``\texttt{-cl-fast-relaxed-math}'') to allow LLVM's loop-vectorizer to prove a vector instruction is identical to the corresponding scalar version, in order to achieve vectorization.}
As will be discussed in~\cref{S:future}, \add{it is hoped that use of explicit vector-types (to lessen demands on the LLVM-vectorization module) in combination with some of these changes might solve this issue}, but for the moment POCL is still quite useful as a validation tool.

>>>>

In contrast,~\cref{F:pocl_source} shows the mean run time per condition of deep, shallow and unvectorized OpenCL codes on the POCL runtime, as compared to OpenMP parallelization.
The reasons for this lack of vectorization are quite technical,~\delete{and somewhat outside the scope of this work}however \add{personal communications~\cite{pocl_communication} with the developers of POCL revealed that, briefly speaking, substantial changes are required to the way POCL prepares LLVM intermediate-representation code (specifically, to ensure LLVM properly recognizes uniform vectorization loop-bounds), LLVM's handling of branches (potentially within POCL instructions themselves) and memory access patterns and potentially use of relaxed math (i.e., ``\texttt{-cl-fast-relaxed-math}'') to allow LLVM's loop-vectorizer to prove a vector instruction is identical to the corresponding scalar version, in order to achieve vectorization.}
No speedup is achieved for either vectorization type on either CPU---\add{though we stress that Intel OpenCL runtime achieved vectorization using the same code and hardware}---indeed, the OpenMP case is faster on both CPUs.
As will be discussed in~\cref{S:future}, \add{it is hoped that use of explicit vector-types (to lessen demands on the LLVM-vectorization module) in combination with some of these changes might solve this issue}, but for the moment POCL is still quite useful as a validation tool.
